Simulation Summary Figures

### 2018-08-14 datasets/simulations/simulations-summary.Rmd

resmet <- dplyr::mutate(resmet, signal = ifelse(grepl("varyinges", setting), dist, NA))
resmet <- dplyr::mutate(resmet, dist = ifelse(grepl("^varyinges$", setting), "gaussian", dist))
resmet <- dplyr::mutate(resmet, dist = ifelse(grepl("^varyinges-t$", setting), "t11", dist))
resmet <- dplyr::mutate(resmet, dist = ifelse(grepl("^varyinges-chisq$", setting), "chisq4", dist))
resmet <- dplyr::mutate(resmet, setting = ifelse(grepl("varyinges", setting), "varyinges", setting))
```

@@

>>>>

resmet <- dplyr::mutate(resmet, signal = ifelse(grepl("varyinges", setting), dist, NA))
resmet <- dplyr::mutate(resmet, dist = ifelse(grepl("^varyinges$", setting), "gaussian", dist))
resmet <- dplyr::mutate(resmet, dist = ifelse(grepl("^varyinges-t$", setting), "t11", dist))
resmet <- dplyr::mutate(resmet, dist = ifelse(grepl("^varyinges-chisq$", setting), "chisq4", dist))
resmet <- dplyr::mutate(resmet, setting = ifelse(grepl("varyinges", setting), "varyinges", setting))

resmet <- dplyr::mutate(resmet, pi0 = ifelse(grepl("varyingntests", setting), 90, pi0))
resmet <- dplyr::mutate(resmet, ntests = ifelse(grepl("varyingntests", setting), dist, "n20000"))
resmet <- dplyr::mutate(resmet, ntests = as.numeric(gsub("n", "", ntests)))
resmet <- dplyr::mutate(resmet, dist = ifelse(grepl("varyingntests", setting), "gaussian", dist))
```

@@

# Varying Test Count

We take a look at a sequence of simulation settings where only the total number of hypthesis tests
is varied. We take a look at the false discovery proportion and true positive rate for each method
at a nomial alpha cutoff of 0.05 as the number of tests is changed.

```{r, fig.width = 10, fig.height = 4}
res_ntests <- dplyr::filter(resmet, setting == "varyingntests", alpha == 0.05)

ntests_fdr <- dplyr::filter(res_ntests, key == "FDR") %>%
    ggplot(aes(x = as.factor(ntests), y = mean.info, color = Method, group = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean.info - se.info, ymax = mean.info + se.info), width = 0.1, alpha=0.5) +
    geom_hline(yintercept = 0.05, lty = 2, color = "blue", alpha = 1/2) + 
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    xlab("Number of Tests") +
    scale_y_continuous("FDR", labels = scales::percent) +
    ggtitle("Mean FDR Over 100 Replications") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face = "bold", size = 10),
          plot.title = element_text(face = "bold", size = 14))

ntests_tpr <- dplyr::filter(res_ntests, key == "TPR") %>%
    ggplot(aes(x = as.factor(ntests), y = mean.info, color = Method, group = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean.info - se.info, ymax = mean.info + se.info), width = 0.1, alpha=0.5) +
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    xlab("Number of Tests") + 
    scale_y_continuous("TPR", labels = scales::percent) +
    ggtitle("Mean TPR Over 100 Replications") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face = "bold", size = 10),
          plot.title = element_text(face = "bold", size = 14))

gp <- plot_grid(ntests_fdr + guides(color = FALSE, linetype = FALSE),
                ntests_tpr + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[1:2], ncol = 2)
gp <- plot_grid(gp, get_legend(ntests_tpr), rel_widths = c(1, 1/8))
gp
```

```{r, fig.width = 10, fig.height = 4}
ntests_fdr_diff <- dplyr::filter(res_ntests, key == "FDR") %>%
    ggplot(aes(x = as.factor(ntests), y = mean.diff, color = Method, group = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean.diff - se.diff, ymax = mean.diff + se.diff), width = 0.1, alpha=0.5) +
    geom_hline(yintercept = 0, lty = 2, color = "blue", alpha = 1/2) + 
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    xlab("Number of Tests") + 
    scale_y_continuous("FDR\n(informative - uninformative)", labels = scales::percent) +
    ggtitle("Mean FDR Difference Over 100 Replications") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face = "bold", size = 10),
          plot.title = element_text(face = "bold", size = 14))

ntests_tpr_diff <- dplyr::filter(res_ntests, key == "TPR") %>%
    ggplot(aes(x = as.factor(ntests), y = mean.diff, color = Method, group = Method)) +
    geom_line(aes(linetype = Method), alpha = 0.85) +
    geom_errorbar(aes(ymin = mean.diff - se.diff, ymax = mean.diff + se.diff), width = 0.1, alpha=0.5) +
    geom_hline(yintercept = 0, lty = 2, color = "blue", alpha = 1/2) + 
    scale_linetype_manual(values = lty) + 
    scale_color_manual(values = col) +
    xlab("Number of Tests") + 
    scale_y_continuous("TPR\n(informative - uninformative)", labels = scales::percent) +
    ggtitle("Mean TPR Difference Over 100 Replications") +
    expand_limits(y = 0) +
    theme_classic() +
    theme(axis.title = element_text(face = "bold", size = 10),
          plot.title = element_text(face = "bold", size = 14))

gp <- plot_grid(ntests_fdr_diff + guides(color = FALSE, linetype = FALSE),
                ntests_tpr_diff + guides(color = FALSE, linetype = FALSE),
                labels = LETTERS[3:4], ncol = 2)
gp <- plot_grid(gp, get_legend(ntests_tpr_diff), rel_widths = c(1, 1/8))
gp
```
